### 2017-10-07 game_language/gl.tex
Cleared it up a bit.

\section{Game Semantics}

@@

Our basic game semantics will be the one given in \cite{hoPcf}.  
We first present the Hyland-Ong game semantics.  
Then, we shall enrich the semantics by appending \game{}s on to strategies.

@@

\begin{definition}
  A \emph{justified play} $s$ in an arena $A$ is given by a (finite or infinite) sequence of moves of $A$, together with a \emph{justification pointer} for each non-initial move $a$ occurring in $s$ back to a previous move $b$ such that $b\ts_A a$.  
  In that case, we say that $b$ \emph{justifies} $a$.

  Furthermore, we require that if $s\ne \emptyplay$ then the first move in $s$ is initial.
\end{definition}

\begin{definition}
  We say that a move $a$ \emph{hereditarily justifies} a move $b$ if there is a sequence of justification pointers in $J(s)$ that leads from $b$ to $a$.
\end{definition}

@@

In order to capture the possibility of divergence, we follow \cite{mcCHFiniteND} and extend the usual definition of a strategy as a set of traces by adding in an extra set of positions designating which plays may lead to a divergence.

Blah blah blah blah blah.

>>>>

\section{\game{}-Game Semantics}

@@

Our basic game semantics will be the one given in \cite{hoPcf}.  
The semantics we present will be an enrichment of the Hyland-Ong semantics obtained by attaching \game{}-moves on to a strategy.

@@

@@

We now give our notion of a strategy, which will add the \game{}-theoretic data on to the usual definition of a strategy.  
We fix a set $\P$ of players.

\begin{definition}
  Let $\M$ be a set of \move{}s, and let $\lambda\from\M\to\P$ be a function saying which player makes each move.  We define a function $\lambda\from (M_A+\M)\to\OP\cup \P$ in the obvious way.

  Let $A$ be an arena.  
  A \emph{\game{}-play} in $A$ is a sequence
  \[
    s \in (M_A + \M)^*
    \]
  (where we refer to elements of $M_A$ as $A$-moves and elements of $\M$ as \move{}s) together with a justification pointer from each non-initial $A$-move $a$ to an $A$-move $b$ occurring earlier in the sequence than $a$ such that $b\ts_A a$.  
  We refer to the sequence $s\vert_{M_A}$ of all the $A$-moves in $s$ as the \emph{shadow} of $s$.
  Furthermore, we require that $s$ satisfy the following properties:
  \begin{enumerate}[a)]
    \item The first move in $s$ is an initial move in $A$ (and therefore an $O$-question).
    \item If $tab\prefix s$, where $a$ is a $P$-move in $A$, then $b$ is an $O$-move in $A$.
    \item If $tab\prefix s$, where $a$ is an $O$-move in $A$, then $b$ is either a $P$-move in $A$ or a \move{}.
    \item If $tma\prefix s$, where $m$ is a \move{}, then $a$ is either a \move{} or an $O$-move in $A$.
  \end{enumerate}
\end{definition}

\begin{definition}
  A \emph{\game{}-strategy} $\sigma$ for an arena $A$ is a set $M_\sigma$ of moves, a function $\lambda_\sigma\from \M_\sigma\to\P$ and a set $\sigma$ of \game{}-plays in $A$ satisfying the following rules:
  \begin{enumerate}[a)]
    \item If $s\in\sigma$ and $sa$ is a \game{}-play in $A$ such that $a$ is either an $O$-move in $A$ or a \move{}, then $sa\in\sigma$.
  \end{enumerate}
\end{definition}

  Let $T\subset\P$ be a team of players.  
  Define a partition of $\OP\cup\P$ into two sets $\F_T$ (`friendly') and $\U_T$ (`unfriendly') by
  \begin{gather*}
    \F_T = \{O\} \cup T \\\
    \U_T = \{P\} \cup (\P \setminus T)
  \end{gather*}
